Landscape heterogeneity simulation figures

### 2018-05-25 Manuscript_figures_2017_12_12.Rmd
Updated Fig 3 label sizing

## Figure 3
```{r}
#percep=3, rec_rate=0.1, density=0.5
p3r0.1d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.1 & merged_data$density==0.5),]
ii<- ggplot(data=p3r0.1d0.5, aes(x=betas, y=max_prevalence,fill=as.factor(beta2)))
ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence", fill= expression(beta[2]))
ii<- ii+ theme(plot.title = element_text(size=7))
ii<- ii+ theme(axis.title = element_text(size=6))
ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=6))
ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
ii<- ii + theme(strip.text = element_text(vjust=0.5, size=6)) 
ii<- ii + theme(legend.text = element_text(vjust=0.5, size=6), legend.title=element_text(vjust=0.5, size=6))
ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
ii<- ii + theme(plot.margin=unit(c(0.1,0.1,0,0.1), "cm"))
ii

jj<- ggplot(data=p3r0.1d0.5, aes(x=betas, y=duration, fill=as.factor(beta2)))
jj<- jj+ geom_boxplot()+ facet_grid( p~ H)
jj<- jj+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Duration", fill= expression(beta[2]))
jj<- jj+ theme(plot.title = element_text(size=7))
jj<- jj+ theme(axis.title = element_text(size=6))
jj<- jj + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=6))
jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=6)) 
jj<- jj + theme(strip.text = element_text(vjust=0.5, size=6)) 
jj<- jj + theme(legend.text = element_text(vjust=0.5, size=6), legend.title=element_text(vjust=0.5, size=7))
jj<- jj + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
jj<- jj + theme(plot.margin=unit(c(-0.1,0.1,0,0.1), "cm"))
jj

prow <- plot_grid( ii + theme(legend.position="none"),
            jj + theme(legend.position="none"),
           align = 'vh',
           labels = c("(A)", "(B)"),
           hjust = -1,
           nrow = 2, label_size=7
           )

@@

tiff("Figure3test.tiff", height = 22.7, width = 17.8, units = "cm", compression = "lzw", res = 900)
#multiplot(ii,jj, cols=1)
p
dev.off()
```

>>>>

## Figure 3
```{r}
#percep=3, rec_rate=0.1, density=0.5
p3r0.1d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.1 & merged_data$density==0.5),]
ii<- ggplot(data=p3r0.1d0.5, aes(x=betas, y=max_prevalence,fill=as.factor(beta2)))
ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence", fill= expression(beta[2]))
ii<- ii+ theme(plot.title = element_text(size=12))
ii<- ii+ theme(axis.title = element_text(size=11))
ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=10))
ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=10)) 
ii<- ii + theme(strip.text = element_text(vjust=0.5, size=11)) 
ii<- ii + theme(legend.text = element_text(vjust=0.5, size=11), legend.title=element_text(vjust=0.5, size=11))
ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
ii<- ii + theme(plot.margin=unit(c(0.1,0.1,0,0.1), "cm"))
ii

jj<- ggplot(data=p3r0.1d0.5, aes(x=betas, y=duration, fill=as.factor(beta2)))
jj<- jj+ geom_boxplot()+ facet_grid( p~ H)
jj<- jj+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Duration", fill= expression(beta[2]))
jj<- jj+ theme(plot.title = element_text(size=12))
jj<- jj+ theme(axis.title = element_text(size=11))
jj<- jj + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=10))
jj<- jj + theme(axis.text.y = element_text(vjust=0.5, size=10)) 
jj<- jj + theme(strip.text = element_text(vjust=0.5, size=11)) 
jj<- jj + theme(legend.text = element_text(vjust=0.5, size=11), legend.title=element_text(vjust=0.5, size=11))
jj<- jj + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
jj<- jj + theme(plot.margin=unit(c(-0.1,0.1,0,0.1), "cm"))
jj

prow <- plot_grid( ii + theme(legend.position="none"),
            jj + theme(legend.position="none"),
           align = 'vh',
           labels = c("(A)", "(B)"),
           hjust = -1,
           nrow = 2, label_size=11
           )

@@

tiff("Figure3new.tiff", height = 22.7, width = 17.8, units = "cm", compression = "lzw", res = 900)
#multiplot(ii,jj, cols=1)
p
dev.off()
```
